% Academic CV — Wilson Style
% Fengming Liu
\documentclass[11pt, a4paper]{article}

% ─── Fonts & Encoding ────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ebgaramond}
\usepackage[scaled=0.85]{beramono}

% ─── Layout ──────────────────────────────────────────────────────
\usepackage[top=0.75in, bottom=0.75in, left=1in, right=1in]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ─── Utilities ───────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{datetime2}

% ─── Hyperlinks (with URL line breaking) ─────────────────────────
\PassOptionsToPackage{hyphens}{url}
\usepackage[hidelinks]{hyperref}
\definecolor{linkblue}{RGB}{0,51,153}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}
\urlstyle{same}
% Allow URLs to break at any character
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

% ─── Section formatting ─────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{4pt}

\titleformat{\subsection}
  {\normalsize\bfseries\raggedright}{}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{2pt}

% ─── Footer ──────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\footnotesize\textcolor{gray}{Fengming Liu — Curriculum Vitae}}
\fancyfoot[R]{\footnotesize\textcolor{gray}{\thepage\ of \pageref{LastPage}}}

% ─── Custom entry command ────────────────────────────────────────
\newlength{\datelength}
\setlength{\datelength}{2.4cm}
\newlength{\contentlength}
\setlength{\contentlength}{\dimexpr\textwidth-\datelength-0.4cm\relax}

\newcommand{\cventry}[2]{%
  \noindent
  \begin{minipage}[t]{\datelength}
    \raggedright #1
  \end{minipage}%
  \hspace{0.4cm}%
  \begin{minipage}[t]{\contentlength}
    \raggedright #2
  \end{minipage}%
  \par\vspace{6pt}%
}

% ══════════════════════════════════════════════════════════════════
\begin{document}

% ─── Header ──────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Fengming Liu}\par\vspace{4pt}
  Department of Political Science, University College London\\
  Gower Street, London WC1E 6BT, United Kingdom\par\vspace{2pt}
  \href{mailto:liu_fengming@outlook.com}{liu\_fengming@outlook.com}
  \enspace$\cdot$\enspace +44\,7436\,241983
  \enspace$\cdot$\enspace ORCID: \href{https://orcid.org/0009-0009-3881-496X}{0009-0009-3881-496X}\\
  \href{https://lfm097384.github.io/liufengming.me/}{lfm097384.github.io/liufengming.me}
\end{center}

% ─── Research Interests ──────────────────────────────────────────
\section{Research Interests}
AI-augmented qualitative research methods, computational text analysis, political economy of technology, and consumer behavior in digitally mediated markets.

% ─── Education ───────────────────────────────────────────────────
\section{Education}

\cventry{2023 -- 2026 (expected)}{%
  \textbf{BSc Philosophy, Politics and Economics}\\
  University College London, Department of Political Science}

\cventry{2020 -- 2023}{%
  \textbf{High School Diploma}\\
  Experimental High School Attached to Beijing Normal University}

% ─── Research Experience ─────────────────────────────────────────
\section{Research Experience}

\cventry{2025 -- Present}{%
  \textbf{Research Assistant}, University College London\\
  Supervisor: Dr.\ Handi Li\\
  Project: Quantitative Analysis of Political Discourse on Social Media}

\cventry{2024 -- Present}{%
  \textbf{Research Assistant}, BI Norwegian Business School \& HEC Paris\\
  Supervisor: Dr.\ Shubin Yu\\
  Project: Generative AI for Research Initiative (\href{https://www.gaiforresearch.com/about}{Project Website})\\
  Conducted interviews, designed questionnaires, co-developed \href{https://mimitalk.app}{\textit{mimitalk.app}} (an AI-powered interview platform), drafted papers.}

\cventry{2024 -- 2026}{%
  \textbf{Research Assistant}, Anhui University\\
  Supervisor: Dr.\ Shun Wang\\
  Data collection and processing, literature review and synthesis.}

% ─── Publications ────────────────────────────────────────────────
\section{Publications}

\subsection{Published}

\begin{enumerate}[leftmargin=1.5em, itemsep=6pt]

  \item Huang, Y., Shu, M., \textbf{Liu, F.}, Liu, B., Huang, C., \& Wang, S.
  ``Nonlinear Heterogeneity Impact of El Ni\~{n}o-Southern Oscillation on Energy
  Markets: A Global Perspective Analysis.''
  \textit{Energy} (2025): 137475.
  \href{https://doi.org/10.1016/j.energy.2025.137475}{doi:10.1016/j.energy.2025.137475}.\\
  \textit{Corresponding Author: Baoliu Liu.}

  \item Shu, M., Wang, C., \textbf{Liu, F.} et al.
  ``The Risk Transmission Mechanism of Global Stock Markets from the Perspective
  of Entropy-Riemann Geometry: Theoretical Construction and Empirical Analysis.''
  \textit{Computational Economics} (2025).
  \href{https://doi.org/10.1007/s10614-025-10913-4}{doi:10.1007/s10614-025-10913-4}.\\
  \textit{Corresponding Author: Fengming Liu.}

\end{enumerate}

\subsection{Preprint}

\begin{enumerate}[leftmargin=1.5em, itemsep=6pt]

  \item \textbf{Liu, F.}, \& Yu, S.
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''
  \textit{arXiv} (2025).
  \href{https://doi.org/10.48550/arXiv.2511.03731}{doi:10.48550/arXiv.2511.03731}.
  Earlier version available at SSRN:
  \href{https://dx.doi.org/10.2139/ssrn.5120349}{10.2139/ssrn.5120349}.\\
  Designated as a Recent Top Paper by SSRN
  (Frontiers in Information Systems Research \& Applications eJournal),
  April 2025.\\
  \textit{Corresponding Author: Shubin Yu.}

\end{enumerate}

\subsection{Working Papers}

\begin{enumerate}[leftmargin=1.5em, itemsep=6pt]

  \item Shu, M., \textbf{Liu, F.}, \& Wang, S.
  ``Cannon to Kilowatts: The Enduring Legacy of the Self-Strengthening
  Movement on China's Electrification.''
  R\&R at \textit{Cliometrica}.\\
  \textit{Corresponding Author: Mingyu Shu.}

\end{enumerate}

% ─── Conference Presentations ───────────────────────────────────
\section{Conference Presentations}

\cventry{2026}{%
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''\\
  COMPTEXT 2026 --- The 8th International Interdisciplinary Conference on Computational Text Analysis. Oral presentation (accepted).}

\cventry{2025}{%
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''\\
  HumanTech Summit 2025 Conference. Oral presentation (presented by F.\ Liu).}

\cventry{2025}{%
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''\\
  Wharton ``Business and Gen AI'' Conference. Oral presentation (presented by S.\ Yu).}

\cventry{2025}{%
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''\\
  Biz AI Conference: AI Applications in Business Research. Poster presentation.}

\cventry{2025}{%
  ``MimiTalk: Revolutionizing Qualitative Research with Dual-Agent AI.''\\
  AMA Summer Academic Conference 2025. Poster presentation.}

\cventry{2025}{%
  ``Cannon to Kilowatts: The Enduring Legacy of the Self-Strengthening Movement on China's Electrification.''\\
  The Eleventh Annual Symposium on Quantitative History. Oral presentation (presented by M.\ Shu).}

% ─── Languages & Skills ──────────────────────────────────────────
\section{Languages and Skills}

\textbf{Languages:} Mandarin (Native), English (Fluent), French (Basic)\\
\textbf{Programming:} C, Javascript, Python, SQL, \LaTeX, AI-assisted Development

\vfill
\begin{center}
  \footnotesize\textcolor{gray}{Last updated: \today}
\end{center}

\end{document}
